### 2020-09-15 LaTeX/sections/paper.tex
some more edits

\paragraph{Front-running.} The primary motivation for using a call market, as opposed to a continuous time orderbook, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}. Consider a sequence of 100 orders submitted within a window of time to market A, and the same sequence randomly shuffled and submitted to market B. If A and B are continuous, the orders that are executed in A could be quite different from B. In a call market, the outcome of A and B will be exactly equivalent. For this reason, there is no threat from miners reordering transactions or users offering higher gas rates to have their orders executed before other orders already broadcast to the network.

In a traditional call market, a market clearing price is chosen and all trades are executed at this price. All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a price improvement. A miner about to mine on a set of transactions, including orders, could insert its own orders that make arbitrage profit by lowering the other traders' price improvements. For this reason, in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}). This does not actively hurt traders---they always receive the same price from their order---and it removes any incentive to front-run these profits.

Potential for front-running still exists around ties on price and cancelations (see below). Finally, \textit{displacement attacks}~\cite{eskandari2019sok} are possible where competitive orders are delayed long enough for the market to close without them. For all these reasons, we say \cm reduces front-running attacks but stop short of saying it is completely solved by \cm.

@@

\begin{itemize}
% = = = = = = = = = = = =How to enforce time on on the Ethereum blockchain? = = = = = = = = = = = = =  %

\item\textbf{{Enforcing Time on the Blockchain.}}

@@

\item\textbf{{Who Pays the Cost for Closing and Reopening the Market?}}

@@

%= = = = = = Miners Close the Market = = = = = = =%
\item \textbf {Miners Close and Reopen the Market.} The difference between the best bid and ask prices is called the \textit{bid-ask spread}. In our design, when the trade occurs between the the highest bid (the highest amount a buyer is willing to pay for an asset) and lowest ask (the lowest amount a seller is willing to accept for an asset) orders, the bid-ask spread is paid to the miner. There are possibilities that (i) no trade occurs or (ii) the bid-ask spread is zero (\ie the best bid and best ask prices are identical). So there is enough economic incentive for the the miner to execute the \texttt{CloseMarket()} function and get refunded as the refund amount could be potentially higher than the bid-ask spread. 
% = = = = = = = = = =Processing Orders in Groups= = = = = = = = = = = = = = = %

\item \textbf{Processing Orders in Groups.} Another solution pattern is to process certain number of bid and ask orders upon every execution of the \texttt{CloseMarket()} function rather than treating them as one substantial transaction. A market participant $P_i$ would process $n$ orders from the previous market (\texttt{CloseMarket(n)}) when sending new orders to the current market. This process continues until all the orders in the previous markets are processed. % incentive? => contribution to the community!?
%= = = = = =  = =  =  Meta txs =  = = = = = = = = =%

\item \textbf {Using the Meta Transactions.} Meta transactions enable users to execute Ethereum functions without paying the gas. Rather than spending gas, users sign their intended action using their private keys and broadcast it to the network with no cost. A third party process (\textit{a relayer}) then crafts the actual transaction on user's behalf, sends the transaction to the Ethereum blockchain, and charges the base contract with the associated fees (see Figure~\ref{fig:meta_tx}). The required gas to pay for the \texttt{Match()} function could be collected as fees. So market participants are charged with certain amounts of fees every time they submit an order, these fees are accumulated in the CallMarket contract and will be used to pay for executing the \texttt{CloseMarket()} function.

@@

\item \textbf{Using the "Contract Pays" Model.} An alternative solution is to design the market such that the last person to submit an order calls the \texttt{CloseMarket()} function, but in contrast to a normal transaction (where the person initiating the transaction must pay the fee), here the CallMarket contract pays the cost for closing the market and matching the orders respectively. To enforce this design we can use Solidity function modifiers; every time a new order is submitted, a function modifier checks whether (i) the auction period has to end and/or (ii) the maximum number of total orders has reached. If any of these two conditions are met, the \texttt{CloseMarket()} will be called. Again, market participants are charged with certain amounts of fees every time they submit an order, these fees are accumulated in the CallMarket. Once the \texttt{CloseMarket()} is successfully executed and orders are matched, the contract transfers its funds to that person. Note that here the person must still have enough gas to cover the execution of the transaction as the funds will be only transferred after the transaction is fully executed. However, market participants are incentivized to do so as they may receive more ethers than they have spent.

@@

\label{sec:rollups}
\item \textbf{Using Rollups.} Rollup is a scaling method that moves the storage and computation of the smart contracts off-chain while maintaining the transaction data on the main chain as call-data. In this technique, any Ethereum user can act as a validator; they can execute the \texttt{CloseMarket()}function and only post the new state of the contract (the updated balance of traders) in the form of \textit{assertions} to the main chain. Rollups improve scalability, provide faster and cheaper execution of the contracts, and eliminate the gas limit as the contract is no longer executed on-chain.
In the followings we briefly discuss different rollup proposals and techniques. Each approach uses a different method to ensure correction of assertions:

\item \textbf{{Non-interactive Rollups.}} In this rollup technique, assertions are posted together with a validity proof that would be later used by validators to check if the \texttt{CloseMarket()} function has been executed correctly. ZK-Rollup scheme is one of the solutions that uses ZK-SNARKs to prove the validity of the assertions in zero-knowledge. ZK proofs are quick and cheap to verify but they are expensive and time consuming to generate. These proofs could be generated (i) for free or (ii) the CallMarket contract could collect proportional fees for every trade that is successfully executed.

\item \textbf{{Optimistic Rollups.}} In this scheme, assertions are assumed to be valid if there is no dispute posted about them with a certain window of time (a.k.a. "the challenge period'). Here, dispute resolution is a gas-costly method as the CallMarket contract would have to emulate the transaction on-chain to ensure the correctness the assertion. This scheme introduces a tradeoff between privacy and performance as all the assertions are publicly available and accessible. However, here the new state only reflects the updated balances of traders and no secret is involved.

\item \textbf {{Multi-round Interactive Rollups.}} In this design paradigm, \textit{pending assertions} are posted on-chain and they are open to dispute. Once the challenge period is over and no challenge is submitted, the assertion is confirmed and the CallMarket contract transitions to the new state (\ie updates traders' balances). This scheme takes the overhead for the CallMarket contract to execute the \texttt{Close()} on-chain by using rounds to the dispute resolutions. The two parties (asserter and challenger) must run an interactive protocol and the CallMarket smart contract would have to act as a referee and decides which party's claim is true. Arbitrum is an example of multi-round interactive rollups that uses an efficient challenge-based protocol to penalize the dishonest parties~\cite{kalodner2018arbitrum}.

\end{itemize}

@@

\item \textbf{{Using Trusted Execution Environments.}} Another way of achieving execution of the \texttt{CloseMarket()} function is incorporating the Ethereum blockchain into the Trusted Execution Environments (TEEs) and decoupling the contract execution from consensus mechanism. TEEs enable secure execution of applications in an isolated processing environment called the \textit{enclave}. Here, the enclave could execute the \texttt{CloseMarket()} function off-chain in TEEs and publish an on-chain attestation Quote to the CallMarket contract. The contract then verifies the correctness of the Quote and if validated correctly, it transitions to the new state. Ekiden is an example that uses Intel SGX to solve the scalability and confidentiality issues with the smart contract execution~\cite{cheng2019ekiden}. A drawback of this scheme is in order to achieve confidentiality-preserving smart contracts we have to trust a trusted party in the form of the hardware manufacturer (\eg Intel).

\end{itemize}
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
\end{itemize}

@@

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

% = = = = = = = = = = = =Notes Discussed in Meetings = = = = = = = = = = = = =  %

% Our two competitors are Uinswap and Loopring (that uses ZK roll ups):
% 	1- Uniswap: we can argue that in traditional markets we have various traditional exchanges. Each of these exchanges have different trading rules and designs which work for different traders.
%	2- Loopring:
%		2-1: Barrier to entry: In order for a trader to trade specific ERC20 on Loopring, Loopring has to agree to support that token. It might not be difficult and they probably approve the token as long as it is standard compliant.
%		2-2: ZK proofs are quick and cheap to verify but they are expensive and time consuming to generate: (1) now they are generating these proofs for free but later they charge traders for doing that. (2) Looping does not probably generate these proofs per every block so the settlement and 				clearing is not happening per block. So we have faster clearing and settlement as we clear everything per block. 
% 		2-3: Loopring is non-custodial, meaning that the money moves only when the proofs come, so there is a latency in transferring funds to the traders.

% The heap with dynamic array can do 26 pairs of matches at worst case matching whereas Linkedliat does 90 pairs. So if we want to cap the orders over 4 PQs, we’re basically increasing the heap size which makes match more expensive for nothing (every time a match happens and the root is deleted the whole heap is reheapified)

% There will be no ties as we use 2 counters for buy and sell orders. These counters are concatenated them with the price. So we somehow enforce time priority

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
%The tables I changed after estimateGas, Not sure which ones to keep. Should talk to Jeremy

%
%% = = = = = = = = = = = =Gas costs and refunds for Dequeueing 50 integers from each PQ  = = = = = = = = = = = = =  %
%
%\begin{table}[]
%\centering
%\begin{tabular}{|c|c|c|c|c|}
%\hline
%
%\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost\\in Gas}}      & \textbf{\thead{Total Cost\\in Gas\\(From \texttt{estimateGas})}}      & \textbf{The Difference}    & \textbf{\thead{Gas Refund \\(Manually Calculated)}} \\ \hline
%
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
%	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,518,131               & 3,283,480		& 765,349             & 750,000                       \\ \hline
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
%	\textbf{\thead{Heap with \\ Static Array}}           				& 1,385,307                & 2,150,625     	& 765,318             & 750,000                      \\ \hline
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
%	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,781,684                & 4,316,229       	& 1,534,545           & 1,500,000                     \\ \hline
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
%	\textbf{Linked List}                       							& 557,085               	& 1,772,085      	& 1,215,000           & 1,200,000                      \\ \hline
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
%	\textbf{\thead{Linked List with \\ Mapping}}          				& 731,514              	& 3,731,514       	& 3,000,000     	  &  3,765,000                       \\ \hline
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
%
%\end{tabular}
%\caption{\footnotesize{The gas metrics associated with dequeuing 50 items from five priority queues.}
%\label{tab:PQUnitTests}}
%\end{table}
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
%
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
%\begin{table}[]
%\begin{tabular}{|c|c|c|c|c|}
%\hline
%\multirow{2}{*}{Gas Metrics}                        							& \multicolumn{2}{c|}{Linked List}           						& \multicolumn{2}{c|}{Linked List with Mapping}     					\\ \cline{2-5} 
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
%                                                                						& with \texttt{SELFDESTRUCT} 		& without \texttt{SELFDESTRUCT}                	& with \texttt{delete} 		& without \texttt{delete}              		\\ \hline                                                                                                                                                                                                                                                          % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
%                   Net Cost in Gas                          					& 557,085                    			& 721,370                     				& 731,514                     	& 334,689                      				\\ \hline
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
%\thead{Total Cost in Gas \\ (from \texttt{estimateGas})} 		& 1,772,085                  			& 736,370                  					& 3,731,514                     	& 1,099,689                       				\\ \hline
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
%		    The Difference                                             		& 1,215,000                  			& 15,000                      				& 3,000,000                    	& 765,000                       				\\ \hline
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
%
%\end{tabular}
%\caption{\footnotesize{}
%\label{tab:LLvsLLMapping}}
%\end{table}
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

%======================================== %

@@

>>>>

\paragraph{Front-running.} The primary motivation for using a call market, as opposed to a continuous time orderbook, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}. Consider a sequence of 100 orders submitted within a window of time to market A, and the same sequence randomly shuffled and submitted to market B. If A and B are continuous, the orders that are executed in A could be quite different from B. In a call market, the outcome of A and B will be exactly equivalent. For this reason, there is no threat from miners reordering transactions or users offering higher gas rates to have their orders executed before other orders already broadcasted.

Potential for front-running still exists around ties on price and cancelations (see below). Finally, \textit{displacement attacks}~\cite{eskandari2019sok} are possible where competitive orders are delayed long enough for the market to close without them. In a traditional call market, a market clearing price is chosen and all trades are executed at this price. All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a price improvement. A miner about to mine on a set of transactions, including its own orders, could drop other traders' orders to maximize its own price improvement. For this reason, in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}). This does not actively hurt traders---they always receive the same price from their order---and it removes any incentive to front-run these profits. For all these reasons, we say \cm reduces front-running attacks but stop short of saying it is completely solved by \cm.

@@

@@

\subsection{Who Pays the Cost for Closing and Reopening the Market?}

@@

%= = = = = = Miners Close the Market = = = = = = =%
\paragraph{Miners Close and Reopen the Market.} The difference between the best bid and ask prices is called the \textit{bid-ask spread}. In our design, when the trade occurs between the the highest bid (the highest amount a buyer is willing to pay for an asset) and lowest ask (the lowest amount a seller is willing to accept for an asset) orders, the bid-ask spread is paid to the miner. There are possibilities that (i) no trade occurs or (ii) the bid-ask spread is zero (\ie the best bid and best ask prices are identical). So there is enough economic incentive for the the miner to execute the \texttt{CloseMarket()} function and get refunded as the refund amount could be potentially higher than the bid-ask spread. 
% = = = = = = = = = =Processing Orders in Groups= = = = = = = = = = = = = = = %

\paragraph{Processing Orders in Groups.} Another solution pattern is to process certain number of bid and ask orders upon every execution of the \texttt{CloseMarket()} function rather than treating them as one substantial transaction. A market participant $P_i$ would process $n$ orders from the previous market (\texttt{CloseMarket(n)}) when sending new orders to the current market. This process continues until all the orders in the previous markets are processed. % incentive? => contribution to the community!?
%= = = = = =  = =  =  Meta txs =  = = = = = = = = =%

\paragraph{Using the Meta Transactions.} Meta transactions enable users to execute Ethereum functions without paying the gas. Rather than spending gas, users sign their intended action using their private keys and broadcast it to the network with no cost. A third party process (\textit{a relayer}) then crafts the actual transaction on user's behalf, sends the transaction to the Ethereum blockchain, and charges the base contract with the associated fees (see Figure~\ref{fig:meta_tx}). The required gas to pay for the \texttt{Match()} function could be collected as fees. So market participants are charged with certain amounts of fees every time they submit an order, these fees are accumulated in the CallMarket contract and will be used to pay for executing the \texttt{CloseMarket()} function.

@@

\paragraph{Using the "Contract Pays" Model.} An alternative solution is to design the market such that the last person to submit an order calls the \texttt{CloseMarket()} function, but in contrast to a normal transaction (where the person initiating the transaction must pay the fee), here the CallMarket contract pays the cost for closing the market and matching the orders respectively. To enforce this design we can use Solidity function modifiers; every time a new order is submitted, a function modifier checks whether (i) the auction period has to end and/or (ii) the maximum number of total orders has reached. If any of these two conditions are met, the \texttt{CloseMarket()} will be called. Again, market participants are charged with certain amounts of fees every time they submit an order, these fees are accumulated in the CallMarket. Once the \texttt{CloseMarket()} is successfully executed and orders are matched, the contract transfers its funds to that person. Note that here the person must still have enough gas to cover the execution of the transaction as the funds will be only transferred after the transaction is fully executed. However, market participants are incentivized to do so as they may receive more ethers than they have spent.

@@

\subsection{Off-Chain Closing}
\label{sec:rollups}

\paragraph{Using Rollups.} Rollup is a scaling method that moves the storage and computation of the smart contracts off-chain while maintaining the transaction data on the main chain as call-data. In this technique, any Ethereum user can act as a validator; they can execute the \texttt{CloseMarket()}function and only post the new state of the contract (the updated balance of traders) in the form of \textit{assertions} to the main chain. Rollups improve scalability, provide faster and cheaper execution of the contracts, and eliminate the gas limit as the contract is no longer executed on-chain.
In the followings we briefly discuss different rollup proposals and techniques. Each approach uses a different method to ensure correction of assertions:

\paragraph{Non-interactive Rollups.} In this rollup technique, assertions are posted together with a validity proof that would be later used by validators to check if the \texttt{CloseMarket()} function has been executed correctly. ZK-Rollup scheme is one of the solutions that uses ZK-SNARKs to prove the validity of the assertions in zero-knowledge. ZK proofs are quick and cheap to verify but they are expensive and time consuming to generate. These proofs could be generated (i) for free or (ii) the CallMarket contract could collect proportional fees for every trade that is successfully executed.

\paragraph{Optimistic Rollups.} In this scheme, assertions are assumed to be valid if there is no dispute posted about them with a certain window of time (a.k.a. "the challenge period'). Here, dispute resolution is a gas-costly method as the CallMarket contract would have to emulate the transaction on-chain to ensure the correctness the assertion. This scheme introduces a tradeoff between privacy and performance as all the assertions are publicly available and accessible. However, here the new state only reflects the updated balances of traders and no secret is involved.

\paragraph{{Multi-round Interactive Rollups.}} In this design paradigm, \textit{pending assertions} are posted on-chain and they are open to dispute. Once the challenge period is over and no challenge is submitted, the assertion is confirmed and the CallMarket contract transitions to the new state (\ie updates traders' balances). This scheme takes the overhead for the CallMarket contract to execute the \texttt{Close()} on-chain by using rounds to the dispute resolutions. The two parties (asserter and challenger) must run an interactive protocol and the CallMarket smart contract would have to act as a referee and decides which party's claim is true. Arbitrum is an example of multi-round interactive rollups that uses an efficient challenge-based protocol to penalize the dishonest parties~\cite{kalodner2018arbitrum}.

@@

\paragraph{{Using Trusted Execution Environments.}} Another way of achieving execution of the \texttt{CloseMarket()} function is incorporating the Ethereum blockchain into the Trusted Execution Environments (TEEs) and decoupling the contract execution from consensus mechanism. TEEs enable secure execution of applications in an isolated processing environment called the \textit{enclave}. Here, the enclave could execute the \texttt{CloseMarket()} function off-chain in TEEs and publish an on-chain attestation Quote to the CallMarket contract. The contract then verifies the correctness of the Quote and if validated correctly, it transitions to the new state. Ekiden is an example that uses Intel SGX to solve the scalability and confidentiality issues with the smart contract execution~\cite{cheng2019ekiden}. A drawback of this scheme is in order to achieve confidentiality-preserving smart contracts we have to trust a trusted party in the form of the hardware manufacturer (\eg Intel).

@@

@@

Imagine you have just launched an ERC20 token on Ethereum. Now want your holders to be able to trade it. While the barrier to entry for exchange services is low, it still exists. For a centralized or decentralized exchange, you have to convince the operators to list your token and you will be delayed while they process your request. For an automated market maker, you will have to lock up a large amount of ETH into the DApp, along with your tokens. For rollups, you will have to list your token, host your own servers, and/or enlist arbitrators. By contrast to all of these, with \cm you just deploy the code alongside your token and trading is immediately supported. Even if \cm is a fallback solution today, we believe it is helpful for every token to be accompanied by on-chain trade execution. And with future improvements to blockchain scalability, it could become the defacto trading method.
